%
% Barren Planet - User Manual
% Main document source
%
% Copyright (C) Damian Gareth Walker 2022
% Manual Sections: The Mission Briefing
%

% Chapter Heading
\chapter{The Mission Briefing}

\noindent
At the start of a campaign, and at the start of each battle, you will be presented with a mission briefing. This tells you what you have to do to win the forthcoming battle.

% Section Heading: The Objective
\section{The Objective}

\noindent
The top right window contains the objective for this mission. In the first mission, it will also include the overall objective of the campaign.

It is important that you read it carefully so that you know what you are supposed to be doing. It will sometimes point out important features of the map, or newly introduced unit types, and contain hints on successfully winning the battle.

% Section Heading: Examining the Map
\section{Examining the Map}

\noindent
The top left window shows part of the map of the battlefield centred on your own forces. You can view the rest of the battlefield by scrolling around it with the cursor control keys.

This offers an opportunity to take in the big picture before you have to focus on individual units and their orders. You will get an idea of the forces at your disposal the enemy that you face, and will also see what kind of terrain you have to navigate.

You can use the information that the map gives you to form an initial strategy to achieve the objective described by the briefing text.

% Section Heading: To Battle!
\section{To Battle!}

\noindent
Once you are done with this overview of the forthcoming battle, you can proceed to action by selecting the {\it Proceed} option from the menu.
