%
% Barren Planet - User Manual
% Main document source
%
% Copyright (C) Damian Gareth Walker 2022
% Manual Sections: Campaigns
%
% Structure:
%

% Chapter Heading
\chapter{Other Campaigns}

% Single Campaign Supplied
\noindent
{\bf \it Barren Planet} is supplied with a single campaign, {\it First Landing}, which tells the story of the two corporations' first arrival at Dapra. But the game supports future expansion and allows for the creation of more campaigns.

% Selecting Future Campaigns
When future campaigns are released, they will be supplied as single files with a {\it .cam} extension. These files need to be copied to the {\bf \it Barren Planet} disk or directory. When the game is next started, there will be a new option available for the {\it Campaign} setting on the {\it New Game} screen.

% New Battles
New campaign expansions will feature new sets of battles. These might further tell the story of Nuvutech and Avuscorp in their battle to control Dapra, or they could instead tell of different corporations, states and empires in a different setting.

% New Unit Types
Unit types are part of the campaign, so future campaigns might also vary the units available. Battle mechs, mega tanks, mobile construction or mining vehicles, self-replicating aliens are all possibilities that the game engine allows.

% New Terrain and Settings
The terrain can also be varied in a new campaign. Perhaps Dapra has ice caps or crystal caves that can be explored in future expansions. Maybe the conflict will expand to airless moons or waterworlds in the system. The {\bf \it Barren Planet} game engine could even handle battles in space itself.

% Single Player Campaigns
The game supports single-player campaigns too. Instead of having the result of one battle dictate which battle is played next, a single-player campaign will have a series of battles in which the human player will only progress when they win a battle. If the human player loses, they re-fight the same battle again. In such a campaign, the side that the human will take is fixed by the campaign's designer.

% Epilogue
Only time will tell on what adventures this game can take you. So keep an eye out in Cyningstan's future catalogues for any {\bf \it Barren Planet} expansions.
