%
% Barren Planet - User Manual
% Main document source
%
% Copyright (C) Damian Gareth Walker 2022
% Manual Sections: The Battle Report
%

% Chapter Heading: The Battle Report
\chapter{The Battle Report}

\noindent
When your opponent has made their move and it is your turn to play, you will naturally want to know what they have been doing. This is where the Battle Report comes in.

The battle report will start by showing the battle map as it was at the start of your opponent's turn. There are two ways you can view the report, both accessed from the menu.

You can play the report through all at once using the {\it Replay} option. If you do this, you will see the whole of your opponent's turn played through at a steady pace. The top left window will show the units moving, attacking, building and repairing. The top right window will contain a panel showing the stats of the enemy unit that is moving, under which will be a report of any attacks that they make. At any time during the report replay, you can hold {\it fire} to bring the menu up again.

Alternatively you can step through your opponent's actions one at a time, by repeatedly choosing the {\it Step} option from the menu. Every move, attack, repair or build will be shown individually. Viewing the report this way takes longer, but it ensures that you don't miss anything if your opponent's turn was particularly eventful.

When you have finished viewing the Battle Report, you can continue to your turn with the {\it Done} menu option. Do this with care: once you proceed to your turn you cannot watch the report again.
